\textsc{LiveRec}: Framing Debug Protocols to Hotwire Probes

### 2023-08-10 paper/paper.tex
Rewrite JDI paragraph

We have developed a debugger capable of stack recording using JDI, a debugging interface for Java. 
A simplified pseudo code of this class is presented in Figure \ref{fig:debugger-class}.
The class includes a method to initialise the JVM (line 2), a method to search or reload a class in the VM (line 5) and a method to generate a stack recording of a method (line 10).

For initialisation, a JVM containing the instrumentation provided by JDI is launched on the KeepAliveAgent class \ref{fig:java-keep-alive-agent} and a breakpoint is set on the infinite loop in the \code{main} function (line 9). 
This breakpoint is used to keep the debugger alive in a wait state, which is necessary to use the JDI primitives \code{mirrorOf}, \code{newInstance} and \code{invokeMethod}.

To load a class, we use a dynamic ClassLoader which allows us to add class paths and load a class during execution. 
When the code changes, the class is reloaded into the KeepAliveAgent. 
This method has one limitation: it only works if the class signature has not changed, and only the contents of the methods have changed. 
If the structure has changed, the KeepAliveAgent must be restarted. 
This limitation can be overcome with certain JVM implementations\cite{KABANOV201151}.

To execute the target method (line 10 in Debugger\ref{fig:debugger-class}), the arguments are created in the client JVM, then passed to the debugger JVM using the \code{mirrorOf} and \code{newInstance} methods of the reflection API (line 11). 
A breakpoint is then placed at the input of the target method (line 12).
The target method is invoked using \code{invokeMethod}. 
Stack recording is then performed using the algorithm described in the previous paragraph. 
As long as the method is not finished, the debugger registers the stackframe and takes a step in the debuggee.

>>>>

To enable stack recording, we developed a debugger leveraging the Java Debug Interface (JDI) library. 
A simplified pseudo-code representation of this debugger is displayed in Figure \ref{fig:debugger-class}. 
The class contains a method for starting the JVM (at line 2), a process to load or reload a class within the VM (at line 5), and a procedure for generating a method stack record (at line 10). Although in practice, the implementation involves multiple interacting threads, these details have been omitted from this overview in favor of clarity and simplicity.

Initialization involves the launch of a JVM that features JDI instrumentation, utilizing the KeepAliveAgent class (in Figure \ref{fig:java-keep-alive-agent}). 
Concurrently, a breakpoint is established at the infinite loop within the \code{main} function, visible at line 9. 
This breakpoint's function is to maintain the debugger in a state of suspension. This waiting state is requisite for the use of JDI primitives such as \code{mirrorOf}, \code{newInstance}, and \code{invokeMethod}.

Class loading is achieved using a dynamic ClassLoader, which gives us the ability to append class paths and load a class during execution. 
Modifications to the code cause the class to be reloaded into the KeepAliveAgent. 
However, there is a caveat to this procedure - it only works if the class signature remains consistent and only the method content is changed. 
Any changes to the structure will require a restart of the KeepAliveAgent. 
It is to be noted that specific JVM implementations can bypass this limitation \cite{}.

To execute a function (line 10 in Debugger class, Figure \ref{fig:debugger-class}), the debugger creates the values associated with the arguments locally. 
It then transmits these values to the JVM containing the KAA using the \code{mirrorOf} and \code{newInstance} methods of JDI's Reflection API (line 11). 
The debugger then sets a breakpoint at the target method's input (line 12) and launches the target method using \code{invokeMethod}. 
The debugger then registers the stack using the algorithm described in the previous paragraph.
Until the method is completed, the debugger registers the stack frame and takes a step forward in debugging.
